\documentclass[longtitle, review, 12pt]{elsarticle}
%\documentclass[3p,sort&compress,times]{elsarticle}
\usepackage[USenglish]{babel}
\usepackage{amsmath}
\usepackage{afterpage}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{ragged2e}
\usepackage{bbm}
\usepackage{bm}
\usepackage[titletoc,toc,title]{appendix}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{lineno}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{proba}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{txfonts}
\usepackage{float}
\usepackage{lineno}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem*{remark}{Remark}
\newtheorem{assumption}{Assumption}
\providecommand{\abs}[1]{\lvert#1\rvert}
\providecommand{\norm}[1]{\lVert#1\rVert}
\DeclareRobustCommand{\1}[1]{\ensuremath \mathbbm{1}_{\{#1\}}}
\journal{Communications in Nonlinear Science and Numerical Simulation}
\captionsetup[subfigure]{style=default, 
    margin=10pt, parskip=0pt, hangindent=0pt, indention=5pt,
    singlelinecheck=false}
%
%
\newcommand{\creflastconjunction}{, and~}
\crefname{hypothesis}{Hypothesis}{Hypotheses}
\DeclareMathOperator{\diag}{diag}
\newcommand{\cqd}{\hfill$\Box$}
\newcommand{\f}{{\mathcal F}}
\newcommand{\IR}{{\mathbb R}}
\newcommand{\IN}{{\mathbb N}}
\newcommand{\ind}{\mbox{\Large$\chi$}}
\newcommand{\tor}{{\mathbb T}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bal}{\begin{align}}
\newcommand{\eal}{\end{align}}
\newcommand{\beqn}{\begin{equation*}}
\newcommand{\eeqn}{\end{equation*}}
\newcommand{\baln}{\begin{align*}}
\newcommand{\ealn}{\end{align*}}
\newcommand{\tbar}{\bar t}
\newcommand{\xbar}{\bar x}
\newcommand{\ep}{\epsilon}
\newcommand{\Pb}{\mathbb P}
\newcommand{\Rl}{\mathbb R}
\newcommand{\tf}{\mathcal{F}}
\newcommand{\hac}{\mathcal{H}}
\newcommand{\hact}{\mathcal{H}_T}
\DeclareMathOperator{\sech}{sech}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\modulolinenumbershttps[1]
\begin{document}
    \begin{frontmatter}
        \title{
            Initial conditions stability of a numerical
            approximation for Kolmogorov equations 
            in infinite dimensions%
        }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \author[add:CONACYT-IMATE]{%
            Francisco Delgado-Vences
        }%
        \ead{delgado@im.unam.mx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \author[add:unison]{%
            Alan Matzumiya-Zazueta
        }%
        \ead{alan.matzumiya@gmail.com}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \author[add:conacyt_unison]{%
            Sa\'ul D\'iaz-Infante
            \corref{corresponding_author}
        }%
        \ead{saul.diazinfante@unison.mx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \address[add:CONACYT-IMATE]{
            CONACYT-UNAM, 
            Instituto de Matem\'aticas, 
            Sede Oaxaca,
            Antonio de Le\'on \#2, altos, Col. Centro,
            Oaxaca de Ju\'arez, CP. 68000
            Phone: +52(951) 5160541
        }
        \address[add:conacyt_unison]{
            CONACYT-Universidad de Sonora, 
            Departamento de Matem\'aticas, Boulevard Luis Encinas y 
            Rosales S/N, 83000, Hermosillo, Sonora, M\'exico.
        }
        \cortext[corresponding_author]{Corresponding author}
%
        \address[add:unison]{
            Universidad de Sonora
            Departamento de Matem\'aticas,
            Departamento de Matem\'aticas. 
            Blvd Luis Encinas y Rosales S/N, 
            Colonia Centro. 
            Edificio 3K-1. C.P. 83000.
            Hermosillo, Sonora, M\'exico,
        }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        \begin{abstract}
                We establish conditions to ensure stability 
            of initial conditions for Kolmogorov equations associated to some 
            kind of stochastic partial differential equations in infinite 
            dimensions. Our approach consists in solving the associated 
            Kolmogorov equation of the underlying SPDE with a spectral method. 
            The numerical solution of the Kolmogorov equation results to be a 
            weak approximation, in probability sense, of a parabolic type of 
            SPDEs. We illustrate our results with numerical experiments. 
		\end{abstract}
		\begin{keyword}
			numerical stability,
			weak approximation,
			Kolmogorov,
			spectral methods,
			SPDs .
		\end{keyword}
	\end{frontmatter}
	%\linenumbers
    \pagebreak
\end{document}